<<<<<<< HEAD
---
title: "R markdown"
author: "林庭誼"
date: "3/18/2020"
output: html_document
---

```{r}
str(example)
pick_above170 <- example$height >= 170
pick_bloodB <- example$bloodType == "B"
pick_loveFood <- 
  stringr::str_detect(example$hobby,"美食")
pick_na <- is.na(example$weight)
pick_after98 <- 
  example$birthday >= lubridate::ymd("1998-01-01")
set_TaipeiMetro <- c("Taipei","New Taipei")
pick_fromTaipeiMetro <- 
  example$residence %in% set_TaipeiMetro
```

```{r}
str(example[c("name","hobby","bloodType")])

example$name[
    pick_loveFood & pick_bloodB
  ]
```
#####誰1998以後出生且住大台北
```{r}
example[c("name","birthday","residence")]

example$name[
  pick_after98 | !pick_fromTaipeiMetro
]
```
#####誰1998以後出生且住大台北且血型B型
```{r}
example$name[
  pick_after98 & pick_fromTaipeiMetro & pick_bloodB
]
```

```{r}
library(stringr)
library(glue)
```
```{r}
install.packages("stringr")
```
```{r}
install.packages("glue")
```


```{r}
str_sub("410873002", 5, 6)
```

```{r}
lubridate::ymd(
  c("民國108年12月5日","民國98年10月5日")
)
```

```{r}
lubridate::ymd(
  c(
    "民國2019年12月05日",
    "馬丁2019的12課05muydifícil",
    "助教2019Emily12解說05真棒",
    "2019R12課程05すごい",
    "R程式2019的12期中考05とても変態"
  )
)
```

```{r}
str_extract_all(
  c("民國108年12月5日","民國98年10月5日"),
  "(?<=民國)[0-9]{2,3}(?=年)"
) # 回傳list 

str_extract(
  c("民國108年12月5日","民國98年10月5日"),
  "(?<=民國)[0-9]{2,3}(?=年)"
) # 回傳vector 
```

